---
title: 'R-Ladies San Diego: Mini RMarkdown Tutorial'
author: "Page Piccinini"
date: "July 13, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load packages
library(tidyverse)
library(forcats)
library(knitr)

# Load function for theme
source("rladiesggplot2theme.R")

# Load data
data_sd = read.csv("rladies_sandiego.csv")
data_global = read.csv("rladies_global.csv")
```

# Introduction

We are going to write about R-Ladies.

# About R-Ladies

## R-Ladies San Diego

R-Ladies San Diego is a group with diverse skill levels, ranging from `r summary(data_sd$level)[1]` beginners to `r summary(data_sd$level)[5]` women how have taught R classes or tutorials.

```{r Level in R, fig.width=10}
ggplot(data_sd, aes(x = level)) +
  geom_bar() +
  r_ladies_theme()
```

```{r Possible topics data, include = FALSE}
data_sd_topics = data_sd %>%
  mutate(topics = strsplit(as.character(topics), ", ")) %>%
  unnest(topics) %>%
  group_by(topics) %>%
  count() %>%
  ungroup()
```

Regarding skill interests, San Diegan R-Ladies are particularly interested in `r arrange(data_sd_topics, desc(n))[1,1]`, `r arrange(data_sd_topics, desc(n))[2,1]`, and `r arrange(data_sd_topics, desc(n))[3,1]`.

```{r Possible topics plot}
ggplot(data_sd_topics, aes(x = reorder(topics, -n), y = n)) +
  geom_bar(stat = "identity") +
  r_ladies_theme() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## R-Ladies Global

R-Ladies currently exists in `r length(unique(data_global$country))` countries. In the United States it exists in `r length(unique(filter(data_global, country == "US")$state))` states. Here is the full list of US based R-Ladies groups.

```{r Global US}
data_us = data_global %>%
  filter(country == "US")

kable(data_us)
```

# Conclusion

R-Ladies is awesome!

